---
title: "p8105_hw6_jz3036"
output: github_document
author: "Junyuan Zheng (jz3036)"
date: 2018-11-17
---

* Import necessary packages.
```{r import_packages}
library(tidyverse)
```

# Problem 1

```{r data_import_p1, message = FALSE}
data_p1 = 
  read_csv(file='./homicide_data/homicide-data.csv')
```

* Create a city_state variable (e.g. “Baltimore, MD”), and a binary variable indicating whether the homicide is solved.
* Omit cities Dallas, TX; Phoenix, AZ; and Kansas City, MO – these don’t report victim race. Also omit Tulsa, AL.
* Modifiy victim_race to have categories white and non-white, with white as the reference category. Be sure that victim_age is numeric.
```{r by_city}
data_p1_city = 
  mutate(data_p1, city_state = paste(city, state, sep = ', '),
                  solved = ifelse(disposition == 
                        'Closed without arrest' | disposition == 'Open/No arrest', 0, 1)) %>%
  filter(., city_state != 'Dallas, TX', city_state != 'Phoenix, AZ',
            city_state != 'Kansas City, MO', city_state != 'Tulsa, AL') %>% 
  mutate(., victim_race_white = ifelse(victim_race == 'White', 'White', 'Non-white'),
            victim_race = fct_relevel(victim_race, "White"),
            victim_age = as.numeric(victim_age))
head(data_p1_city)
```

* For the city of Baltimore, MD, use the glm function to fit a logistic regression with resolved vs unresolved as the outcome and victim age, sex and race (as just defined) as predictors.
* Save the output of glm as an R object; apply the broom::tidy to this object; and obtain the estimate and confidence interval of the adjusted odds ratio for solving homicides comparing black victims to white victims keeping all other variables fixed.
```{r glm_Baltimore}
fit_logistic_Baltimore = 
  filter(data_p1_city, city_state == 'Baltimore, MD') %>% 
  glm(solved ~ victim_age + victim_sex + victim_race, data = ., family = binomial())

fit_logistic_Baltimore %>% 
  broom::tidy(.) %>% 
  mutate(., OR = exp(estimate),
            CI_low = estimate - std.error*qt(0.975, 2820),
            CI_high = estimate + std.error*qt(0.975, 2820),
            exp_CI_low = exp(CI_low),
            exp_CI_high = exp(CI_high)) %>%
  select(., term, OR, exp_CI_low, exp_CI_high) %>%
  filter(., term == 'victim_raceBlack')
```


* Now run glm for each of the cities in your dataset, and extract the adjusted odds ratio (and CI) for solving homicides comparing black victims to white victims. Do this within a “tidy” pipeline, making use of purrr::map, list columns, and unnest as necessary to create a dataframe with estimated ORs and CIs for each city.

```{r glm_all_cities}
fit_logistic_all_cities = 
data_p1_city %>% 
  group_by(., city_state) %>% 
  nest(.) %>% 
  mutate(models = map(data, ~glm(solved ~ victim_age + victim_sex + victim_race,
                                 data = .x, family = binomial())),
         models = map(models, broom::tidy)) %>% 
  select(-data) %>% 
  unnest() %>% 
  mutate(., OR = exp(estimate),
            CI_low = estimate - std.error*qt(0.975, 2820),
            CI_high = estimate + std.error*qt(0.975, 2820),
            exp_CI_low = exp(CI_low),
            exp_CI_high = exp(CI_high)) %>%
  select(., city_state, term, OR, exp_CI_low, exp_CI_high) %>% 
  filter(., term == 'victim_raceBlack')
fit_logistic_all_cities
```

* Create a plot that shows the estimated ORs and CIs for each city. Organize cities according to estimated OR, and comment on the plot.

```{r OR_CI_plot}
fit_logistic_all_cities %>%
  mutate(city_state = fct_reorder(city_state, OR)) %>% 
  ggplot(aes(x = city_state, y = OR)) +
  geom_point(shape = 22, size = 2, fill = 'white') +
  geom_errorbar(aes(ymin = exp_CI_low, ymax = exp_CI_high), colour='red', alpha = 0.8) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.3)) +
  labs(title = 'OR & CI for each city (Black vs. White Victims)') +
  geom_hline(yintercept = 1, alpha = 0.5)
```

As shown by the plot above, all the OR fall in the CI range, which could mean the results are statistically significant if not look at the p-value directly. Most of the OR is lower than 1, which means, compared to white victims, cases with black victims at those cities are less likely to be solved. The only three cities where cases with black victims are more likely to be solved than those having white victims are Birminghan, Durham, and Tampa.
