---
title: "p8105_hw6_jz3036"
output: github_document
author: "Junyuan Zheng (jz3036)"
date: 2018-11-17
---

* Import necessary packages.
```{r import_packages}
library(tidyverse)
```

# Problem 1

```{r data_import_p1, message = FALSE}
data_p1 = 
  read_csv(file='./homicide_data/homicide-data.csv')
```

* Create a city_state variable (e.g. “Baltimore, MD”), and a binary variable indicating whether the homicide is solved.
* Omit cities Dallas, TX; Phoenix, AZ; and Kansas City, MO – these don’t report victim race. Also omit Tulsa, AL.
* Modifiy victim_race to have categories white and non-white, with white as the reference category. Be sure that victim_age is numeric.
```{r by_city}
data_p1_city = 
  mutate(data_p1, city_state = paste(city, state, sep = ', '),
                  solved = ifelse(disposition == 
                        'Closed without arrest' | disposition == 'Open/No arrest', 0, 1)) %>%
  filter(., city_state != 'Dallas, TX', city_state != 'Phoenix, AZ',
            city_state != 'Kansas City, MO', city_state != 'Tulsa, AL') %>% 
  mutate(., victim_race = ifelse(victim_race == 'White', 'White', 'Non-white'),
            victim_race = fct_relevel(victim_race, "White"),
            victim_age = as.numeric(victim_age))
```


